sensiAnPaper1All

### 2016-01-15 effectOfIndividualInputs.Rmd
progressing

  #input files in listOutMix, listOutIn1 & listOutI2 are the same if the runs are done with default randomSeed 
  #except that exposure will be in a.f_AB, a.f_A0 and a.f_B0 respectively (& a.m* too)
  #I could just rename one to exposure
  rownames(treeInput)[rownames(treeInput)=="a.f_AB"] <- "exposure"

@@

  #hardcode which variables to include in the tree analysis here
  #to keep it simple and transparent
  #treePredictors <- c('P_1','P_2','startResistanceRatio','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  #prettifying names
  treePredictors <- c('P_1','P_2','startResistanceRatio','exposure','effectiveness_insecticide1','effectiveness_insecticide2','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  treeInput <- treeInput[ treePredictors, ]

  #get the inputs here to use in ggplot investigation of model responses to inputs
  #used in a later chunk
  ggInput <- treeInput
```

@@

@@

  #exposure has the most noticeable effect
  ggplot(ggInsOuts, aes(x=exposure, y=gen_cP0.25, color=strategy)) + 
    geom_point() + 
    facet_wrap( ~ strategy) + 
    #geom_smooth(aes(x=exposure, y=gen_cP0.5, color=NULL))
    geom_smooth(colour='red', linetype='dashed',size=0.5)

  #effectiveness of insecticide1 little noticeable effect
#   ggplot(ggInsOuts, aes(x=effectiveness_insecticide1, y=gen_cP0.25, color=strategy)) + 
#     geom_point() + 
#     facet_wrap( ~ strategy) + 
#     #geom_smooth(aes(x=effectiveness_insecticide1, y=gen_cP0.5, color=NULL)) 
#     geom_smooth(colour='red', linetype='dashed',size=0.5)

@@

    y <- 'gen_cP0.25'    
    #y <- 'gen_cP0.5'
    #color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    color <- 'exposure'

@@

  #can I facet by particular parameter ranges ?
  #or even subset the data for specific parameter ranges

>>>>

  #input files in listOutMix, listOutIn1 & listOutI2 are the same if the runs are done with default randomSeed 
  #except that exposure will be in a.f_AB, a.f_A0 and a.f_B0 respectively (& a.m* too)
  #I could just rename one to exposure
  #BEWARE risk if future changes
  rownames(treeInput)[rownames(treeInput)=="a.f_AB"] <- "exposure"

  #hardcode which variables to include in analysis to keep it simple and transparent
  treePredictors <- c('P_1','P_2','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')

  treeInput <- treeInput[ treePredictors, ]

@@

  rownames(treeInput)[rownames(treeInput)=="P_1"] <- "start_freq_allele1"
  rownames(treeInput)[rownames(treeInput)=="P_2"] <- "start_freq_allele2"

  rownames(treeInput)[rownames(treeInput)=="h.RS1_A0"] <- "dominance_allele1"
  rownames(treeInput)[rownames(treeInput)=="h.RS2_0B"] <- "dominance_allele2"

  rownames(treeInput)[rownames(treeInput)=="s.RR1_A0"] <- "selection_coef_allele1"
  rownames(treeInput)[rownames(treeInput)=="s.RR2_0B"] <- "selection_coef_allele2"

  #subsetting now done above before names prettified
  #treePredictors <- c('P_1','P_2','startResistanceRatio','exposure','effectiveness_insecticide1','effectiveness_insecticide2','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  #treeInput <- treeInput[ treePredictors, ]

  #get the inputs here to use in ggplot investigation of model responses to inputs
  #used in a later chunk
  ggInput <- treeInput

@@

  #prettify output names
  names(ggInsOuts)[names(ggInsOuts)=="gen_cP0.5"] <- "time_to_resistance0.5"
  names(ggInsOuts)[names(ggInsOuts)=="gen_cP0.25"] <- "time_to_resistance0.25"
  names(ggInsOuts)[names(ggInsOuts)=="gen_cP0.1"] <- "time_to_resistance0.1"

@@

  #exposure has the most noticeable effect
  ggplot(ggInsOuts, aes(x=exposure, y=time_to_resistance0.25, color=strategy)) + 
    geom_point() + 
    facet_wrap( ~ strategy) + 
    #geom_smooth(aes(x=exposure, y=gen_cP0.5, color=NULL))
    geom_smooth(colour='red', linetype='dashed',size=0.5)

  #effectiveness of insecticide1 little noticeable effect
#   ggplot(ggInsOuts, aes(x=effectiveness_insecticide1, y=time_to_resistance0.25, color=strategy)) + 
#     geom_point() + 
#     facet_wrap( ~ strategy) + 
#     #geom_smooth(aes(x=effectiveness_insecticide1, y=gen_cP0.5, color=NULL)) 
#     geom_smooth(colour='red', linetype='dashed',size=0.5)

@@

    y <- 'time_to_resistance0.25'    
    #y <- 'time_to_resistance0.5'
    #color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    color <- 'exposure'

@@

  #can I facet by particular parameter ranges ?
  #might need to create a categorical var from the range and use that to facet 
  #or subset the data for specific parameter ranges

### 2016-01-15 resistanceModelNotesAndy.Rmd
progressing

@@

See sensiAnPaperPartOneAtATime.r
  #TODO I need to think more carefully about how to do this
  #and maybe lookup to see if I can steal any existing sensi analysis type code
  #and look back at my existing notes
1. Graphs where just change one param at a time. Jo Lines/Andy conversation at TAG.

>>>>

** 15/1/16 **
sent first version of ggplot doc (effectOfIndividualInputs.pdf) to Ian & Beth

prettifying parameter names

@@

# try changing plot symbol to open circles
# maybe add in a loop to plot for all 3 resistance thresholds
# maybe try removing reps with num generations 1000 ?
# maybe try faceting by parameter ranges ?
# lookup to see if I can steal any existing sensi analysis type code

See sensiAnPaperPartOneAtATime.r
  #TODO I need to think more carefully about how to do this
  #and look back at my existing notes
1. Graphs where just change one param at a time. Jo Lines/Andy conversation at TAG.

### 2016-01-15 sensiAnPaper1All.Rmd
progressing

```{r}
  ## to load previously saved runs, e.g. these that I added 100 onto filename
  load(file=paste0(outFolder,'listOutMix_1000.rda'))
  load(file=paste0(outFolder,'listOutI1_1000.rda'))
  load(file=paste0(outFolder,'listOutI2_1000.rda'))

@@

  #hardcode which variables to include in the tree analysis here
  #to keep it simple and transparent
  #treePredictors <- c('P_1','P_2','startResistanceRatio','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  #prettifying names
  treePredictors <- c('P_1','P_2','startResistanceRatio','exposure','effectiveness_insecticide1','effectiveness_insecticide2','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  treeInput <- treeInput[ treePredictors, ]

@@

  #uses ggInput calculated in earlier trunk

  #first needs to transpose rows to cols
  ggInput_T <- t(ggInput)

>>>>

```{r}
  ## to load previously saved runs
  load(file=paste0(outFolder,'listOutMix_1000.rda'))
  load(file=paste0(outFolder,'listOutI1_1000.rda'))
  load(file=paste0(outFolder,'listOutI2_1000.rda'))

@@

  rownames(treeInput)[rownames(treeInput)=="P_1"] <- "start_freq_allele1"
  rownames(treeInput)[rownames(treeInput)=="P_2"] <- "start_freq_allele2"

  rownames(treeInput)[rownames(treeInput)=="h.RS1_A0"] <- "dominance_allele1"
  rownames(treeInput)[rownames(treeInput)=="h.RS2_0B"] <- "dominance_allele2"

  rownames(treeInput)[rownames(treeInput)=="s.RR1_A0"] <- "selection_coef_allele1"
  rownames(treeInput)[rownames(treeInput)=="s.RR2_0B"] <- "selection_coef_allele2"

  #subsetting now done above before names prettified
  #treePredictors <- c('P_1','P_2','startResistanceRatio','exposure','effectiveness_insecticide1','effectiveness_insecticide2','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  #treeInput <- treeInput[ treePredictors, ]

@@

  #uses ggInput calculated in earlier chunk

  #first needs to transpose rows to cols
  #ggInput_T <- t(ggInput)
